---
title: "Amazon Review Analysis"
author: Ra'Shawn Howard
output: html_notebook
---

# Data
The Amazon reviews polarity [Data](https://www.kaggle.com/kritanjalijain/amazon-reviews?select=train.csv) is constructed by taking review score 1 and 2 as negative, 4 and 5 as positive. Samples of score 3 are ignored. In the dataset, class 1 is the negative and class 2 is the positive. the training set has 3.6 million observations and test set has 400,000 observations

# Methods

# Results
# Limitations and Next Steps
# Reference
+ [What is Sentiment Analysis](https://brand24.com/blog/sentiment-analysis/)
+ [look at this](https://www.richpauloo.com/post/word-cloud/)
+ [Data](https://www.kaggle.com/kritanjalijain/amazon-reviews?select=train.csv)
+ [Different Models For Data](https://paperswithcode.com/sota/sentiment-analysis-on-amazon-review-polarity)
+ [BERT Model](https://www.geeksforgeeks.org/explanation-of-bert-model-nlp/)
+ [logistic regression gif](https://mlfromscratch.com/machine-learning-introduction-8-linear-regression-and-logistic-regression/#/)
+ [Julia Silge Book](https://www.tidytextmining.com/tidytext.html)
+ [correlation and bigrams](https://www.tidytextmining.com/ngrams.html)
+ [Metrics defined](https://medium.com/@yashwant140393/the-3-pillars-of-binary-classification-accuracy-precision-recall-d2da3d09f664)

```{r set-up}
library(tidyverse)
library(tidymodels)
library(tidytext)

knitr::opts_chunk$set(echo=FALSE, include = FALSE)
theme_set(ggthemes::theme_hc())
```

```{r load-data}
train <- read_csv("/Users/rashawnhoward/Downloads/train-2.csv", col_names = FALSE)
test  <- read_csv("/Users/rashawnhoward/Downloads/test-2.csv",  col_names = FALSE)

train %>% 
  select(-X2) %>% 
  rename(polarity = X1,
         text = X3) %>% 
  mutate(polarity = as.factor(polarity)) -> train

train %>% 
  unnest_tokens(word,text) -> df 

head(df)
tail(df)
```

# Discriptive Statistics
```{r word-counts-and-correlations}


library(wordcloud)
library(reshape2) # for acast() function

# Bar charts

# Top 25 Common Words in entire Dataset
df %>% 
  anti_join(stop_words) %>% 
  count(word,sort=TRUE) %>% 
  head(25) %>% 
  ggplot(aes(reorder(word,n),n)) +
  geom_col(fill="lightblue") +
  coord_flip() +
  labs(x="",
       y = "Count",
       title = "Top 25 Common Words")
    
## Top 25 Common Words by Polarity=1
df %>% 
  anti_join(stop_words) %>% 
  filter(polarity==1) %>% 
  count(word, sort = TRUE) %>% 
  head(25) %>% 
  ggplot(aes(reorder(word,n),n)) +
  geom_col(fill="lightblue") +
  coord_flip() +
  labs(x="",
       y = "Count",
       title = "Top 25 Common Words by Polarity=1")

## Top 25 Common Words by Polarity=2
df %>% 
  anti_join(stop_words) %>% 
  filter(polarity==2) %>% 
  count(word, sort = TRUE) %>% 
  head(25) %>% 
  ggplot(aes(reorder(word,n),n)) +
  geom_col(fill="lightblue") +
  coord_flip() +
  labs(x="",
       y = "Count",
       title = "Top 25 Common Words by Polarity=2")

## Count of Polarity
df %>% 
  anti_join(stop_words) %>% 
  ggplot(aes(polarity)) +
  geom_bar(fill="lightblue") +
  ggtitle("Count of Polarity") +
  expand_limits(x = c(0, NA), y = c(0, NA)) +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
  
```

# Correlation Analysis
```{r bi-grams-graph}
library(widyr)
library(igraph)
library(ggraph)

# Take Sample of 200000 for graphs
sample <- train %>% 
  slice_sample(n=200000)

rm(train)

count_bigrams <- function(dataset) {
  dataset %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(!word1 %in% stop_words$word,
           !word2 %in% stop_words$word) %>%
    count(word1, word2, sort = TRUE)
}

visualize_bigrams <- function(bigrams) {
  set.seed(2016)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void()
}

bigram_count <- count_bigrams(sample)

# filter out rare combinations, as well as digits
bigram_count %>%
  filter(n > 300,
         !str_detect(word1, "\\d"),
         !str_detect(word2, "\\d")) %>%
  visualize_bigrams()
```

examine correlation among words, which indicates how often they appear together relative to how often they appear separately. In particular, here we’ll focus on the phi coefficient, a common measure for binary correlation. The focus of the phi coefficient is how much more likely it is that either both word X and Y appear, or neither do, than that one appears without the other.

Consider the following table: [Table](https://www.tidytextmining.com/ngrams.html)

For example, that n11 represents the number of documents where both word X and word Y appear, n00
the number where neither appears, and n10 and n01 the cases where one appears without the other. In terms of this table, the phi coefficient is: [coefficient](https://www.tidytextmining.com/ngrams.html) The phi coefficient is equivalent to the Pearson correlation

The pairwise_cor() function in widyr lets us find the phi coefficient between words based on how often they appear in the same section.

```{r correlation-graph}

section_words <- sample %>% 
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word)

word_cor <- section_words %>% 
  group_by(word) %>% 
  filter(n() > 20) %>% 
  pairwise_cor(word, section, sort = TRUE)

set.seed(2016)

word_cor %>%
  filter(correlation > .60) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void()

```

# Sentiment Analysis
a token is a meaningful unit of text, most often a word, that we are intrested in for further analysis, and tokenization is the process of splitting text into tokens
+ Use unnest_tokens() for tokenization
stop words are common words such as (the and i ...)
+ Remove stop words with an anti_join()
```{r}
# Sentiment Analysis 
# Comparision Cloud
nums <- df %>% filter(str_detect(word, "^[0-9]")) %>% select(word) %>% unique() # regex to remove numbers

df %>% 
  anti_join(stop_words,by="word") %>% 
  anti_join(nums, by="word") %>% 
  left_join(get_sentiments("bing")) %>% 
  count(word,sentiment,sort=TRUE) %>% 
  na.omit() %>% 
  acast(word~sentiment, value.var = "n",fill=0) %>% 
  comparison.cloud(colors=brewer.pal(3, "Dark2"),
                   max.words = 100)
```

# PreProcess
```{r}
library(textrecipes)

set.seed(2012)
train_sample <- slice_sample(train,n=400000)
rm(train)

rec1 <- recipe(polarity~text,data=train_sample) %>% 
  step_tokenize(text) %>% # Could do n-grams(sentences)
  step_stopwords(text) %>% 
  step_tokenfilter(text,max_tokens = 1000) %>% # only keep 1000 tokens after removing stop words
  step_tf(text) %>% # convert tokens into weights using tf 
  step_normalize(all_predictors()) # model is sensitive to centering and scaling
  

rec2 <- recipe(polarity~text,data=train_sample) %>% 
  step_tokenize(text) %>% # Could do n-grams(sentences)
  step_stopwords(text) %>% 
  step_tokenfilter(text,max_tokens = 1000) %>% # only keep 1000 tokens after removing stop words
  step_tfidf(text) %>% # convert tokens into weights using tfidf (usually outperforms term frequency)
  step_normalize(all_predictors()) # model is sensitive to centering and scaling
```

# Model Data
```{r}
lasso_spec <- logistic_reg(penalty = tune(), mixture = 1) %>%
  set_engine("glmnet")

lasso_wf1 <- workflow() %>% 
  add_recipe(rec1) %>% 
  add_model(lasso_spec)

lasso_wf2 <- workflow() %>% 
  add_recipe(rec2) %>% 
  add_model(lasso_spec)
```

```{r}
lambda_grid <- grid_latin_hypercube(penalty(), 
                                    size=20)

set.seed(123)
folds <- vfold_cv(train_sample)
```

```{r}
doParallel::registerDoParallel()

set.seed(2021)
lasso_grid1 <- tune_grid(
  lasso_wf1,
  resamples = folds,
  grid = lambda_grid
)

set.seed(2021)
lasso_grid2 <- tune_grid(
  lasso_wf2,
  resamples = folds,
  grid = lambda_grid
)
```

```{r}
lasso_grid1 %>% 
  collect_metrics() %>% 
  ggplot(aes(penalty,mean,color=.metric)) +
  geom_line(size=1.5,show.legend = FALSE) +
  facet_wrap(~.metric) +
  scale_x_log10() +
  ggthemes::theme_hc() + 
  ggtitle("tf Model")

lasso_grid2 %>% 
  collect_metrics() %>% 
  ggplot(aes(penalty,mean,color=.metric)) +
  geom_line(size=1.5,show.legend = FALSE) +
  facet_wrap(~.metric) +
  scale_x_log10() +
  ggthemes::theme_hc() + 
  ggtitle("tf_idf Model")
```

```{r}
best_auc <- lasso_grid2 %>% 
  select_best("roc_auc") # get best model based on roc_auc

best_auc # penalty = 0.000134932639820473

final_lasso <- finalize_workflow(lasso_wf2,best_auc)
final_lasso
```

```{r variable-importance-plots}
library(vip)
p2 <- final_lasso %>% 
  fit(train) %>% 
  pull_workflow_fit() %>% 
  vip::vi(lambda = best_auc$penalty) %>% 
  group_by(Sign) %>% 
  top_n(20, wt = abs(Importance)) %>% 
  ungroup() %>% 
  mutate(Importance = abs(Importance),
         Variable = str_remove(Variable,"tfidf_text_"),
         Variable = fct_reorder(Variable,Importance)) %>% 
  ggplot(aes(Importance,Variable,fill=Sign)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~Sign, scales = "free_y")
p2 + ggthemes::theme_hc()
```

```{r final-model-on-train-set}
# Use unaltered train set!
head(train_sample)
rec3 <- recipe(X1~.,train_sample) %>% 
  step_rm(X2) %>% 
  step_rename(polarity = X1,
              text = X3) %>% 
  step_tokenize(text) %>% # Could do n-grams(sentences)
  step_stopwords(text) %>% 
  step_tokenfilter(text,max_tokens = 1000) %>% # only keep 1000 tokens after removing stop words
  step_tfidf(text) %>% # convert tokens into weights using tfidf
  step_normalize(all_predictors())

data <- rec3 %>% 
  prep() %>% 
  bake(new_data=NULL)

head(data)

spec <- logistic_reg(penalty = 0.000134932639820473, mixture = 1) %>% 
  set_engine("glmnet") 

lasso_mod <- fit(spec,
                 factor(polarity)~.,
                 data)

```


# Results
```{r}
head(test)
test_ <- bake(prep(rec3),test)
preds <- predict(lasso_mod,new_data = test_)

test_ %>% 
  select(polarity) %>% 
  mutate(polarity = factor(polarity),
         polarity = ifelse(polarity==1.0009191724383,"positive","negative"),
         polarity = factor(polarity)) %>% 
  bind_cols(preds) %>% 
  mutate(.pred_class = ifelse(.pred_class==1.0009191724383,"positive","negative"),
         .pred_class = factor(.pred_class)) %>% 
  conf_mat(polarity,.pred_class)
```

